### 2016-01-21 01-intro.tex
Polish on 01. Add 06.

One such big data problem is analyzing large graphs such as social networks where it is not unusual to see a network consisting of billions of edges and tens of million of vertices~\cite{yang2015defining}. In particular, we are interested in the overlapping community detection problem~\cite{xie2013overlapping}, where the goal is to learn the probability distribution of each vertex to participate in each community, given a set of vertices, the links between them (which are usually very sparse), and the number of latent communities. A community can be seen as a densely connected group of vertices that are only sparsely connected to the rest of the network.

@@

In this paper, we are particularly interested in the SG-MCMC method applied to the a-MMSB model introduced in \cite{LiAW15}, which turned out to be faster and more accurate than the SVB method. Although \cite{LiAW15} proposed a scalable algorithm for the problem, there is still room to improve the performance further by considering a custom high-performance implementation. To this end, we propose a design of a parallel and distributed system specifically tailored to solve the a-MMSB problem. In particular, we use a mixture of OpenMP, MPI and RDMA in order to efficiently scale and accelerate the algorithm's computation.

>>>>

One such big data problem is analyzing large graphs such as social networks where it is not unusual to see a network consisting of billions of edges and tens of million of vertices~\cite{yang2015defining}. In particular, we are interested in the overlapping community detection problem~\cite{xie2013overlapping}, where the goal is to learn the probability distribution of each vertex to participate in each community, given a set of vertices, the links between them (which are usually very sparse), and the number of latent communities. A community can be seen as a densely connected group of vertices that are only sparsely connected to the rest of the network. This problem is much harder than the related domain of detecting disjoint communities.

@@

In this paper, we are particularly interested in the SG-MCMC method applied to the a-MMSB model introduced in \cite{LiAW15}, which turned out to be faster and more accurate than the SVB method. \cite{LiAW15} further proposes a heuristic to scale up the number of communities at the cost of less precision; the work in this paper scales the algorithm without that heuristic with a custom high-performance implementation. To this end, we propose a design of a parallel and distributed system specifically tailored to solve the a-MMSB problem. In particular, we use a mixture of OpenMP, MPI and RDMA in order to efficiently scale and accelerate the algorithm's computation.
